# Loading and preprocessing the data

### Read the CSV file, and verify that there are all together 17568 obs and 3 variables.

```{r LoadandPreprocessData, echo=TRUE}
act0 <-read.csv(file.path(getwd(), "activity.csv"), header=TRUE, sep=",")
summary(act0)
```

Convert the ```date``` variable to a date class:
```{r LoadandPreprocessData, echo=TRUE}
library(ggplot2)
library(plyr)

act0$date <- as.Date(act0$date) 
str(act0)
'data.frame':  17568 obs. of  3 variables:
 $ steps   : int  NA NA NA NA NA NA NA NA NA NA ...
 $ date    : Date, format: "2012-10-01" "2012-10-01" ...
 $ interval: int  0 5 10 15 20 25 30 35 40 45 ...
```

# What is mean total number of steps taken per day?
### 1.Calculate the total number of steps taken per day
```{r, echo=TRUE}
StepsDaily<-ddply(act0, c("date"),summarise,
                   TotalSteps=sum(steps,na.rm=TRUE)
                   )
```

### 2.If you do not understand the difference between a histogram and a barplot, research the difference between them. Make a histogram of the total number of steps taken each day

```{r, echo=TRUE}
ggplot(StepsDaily, aes(x = TotalSteps)) + geom_histogram(alpha = 1/2, binwidth = 1000)
```


# What is the average daily activity pattern?

### 1. Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
### 2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r, echo=TRUE}
StepsInterval<-ddply(act0, c("interval"),summarise, MeanSteps=sum(steps,na.rm=TRUE)

ggplot(StepsInterval, aes(x = interval, y = MeanSteps)) + geom_line()
```
### The five minute interval with the highest mean step-count is interval #835 with a mean of 206.1698 steps.

# Imputing missing values
### There are 2304 incomplete records, unevenly distributed through the data.
```{r, echo=TRUE}
hist(which(complete.cases(activity)),
     main="Count of complete cases (chronological order)",
     xlab="Observation number",
     ylab="Count of complete cases"
     )
```
